\section*{Instructions}

This is the written round for the Thomas Jefferson Intermediate Olympiad in Informatics 2017.  This packet contains a series of written problems to be completed during the one ($1$) hour time period.  Once your time has expired, you are no longer permitted to write and must turn in all written solutions to a proctor.
\blank
During this round, you may not use \textbf{any external materials}, including all printed materials, and any electronic or communications devices. Any violation of this rule is grounds for immediate disqualification.
\blank
As a team, you may collaborate among each other. However, you may not communicate with any other teams during the contest window for any reason.
\blank
The style of pseudocode that you write for your solutions is not particularly important, as long as it is understandable. Feel free to use Java or Python syntax, if that's what makes the most sense to you. Note, however, that when we write pseudocode, we follow the convention that in the range $A \dots B$, $A$ is inclusive while $B$ is exclusive. This is equivalent to the Python convention for \verb|range(A, B)|.
\blank
Please use the zero-indexed convention when responding to questions. Responses that are one-indexed will not receive full credit.
\blank
You will write your answer to each problem on a blank sheet of paper. \textbf{You must write your team id on the top left hand corner of each page!}. If you fail to do so, your team will not receive credit for that problem. \textbf{Place the problem number at the top right hand corner of each page. Each problem should go on a separate sheet of paper. Feel free to ask your proctor for more paper if you need it.} 
\blank
\begin{center}
    \textbf{\Large Do not turn the page until instructed to do so.}
\end{center}
