\section*{Instructions}

\blank

\large
\begin{enumerate}
    \item The following section consists of 3 problems, which will not count towards your actual contest score.  The purpose of these problems are to familiarize you with the virtual machine environment and using the grader.
    \item Each problem consists consists of 3 sample input cases of increasing complexity. 10 points are awarded for each input case correctly solved, for a total of 30 points per problem, and 90 points for the entire round.
    \item The first test case will always be the sample case. We may disqualify any programs that consist of only print statements.
    \item Programs must read from standard input and print to standard output. Ensure that your program does not print any extraneous output, such as debug statements.
    \item Unless otherwise stated, programs must run in 2 seconds and in 256 MB of memory.
    \item Accepted languages include Java 8, Python 3, and C/C++. You must submit the source code of your programs, not executable files.
    \item For Java programs, the name of the Java class and the file name should be the short name. For example, a solution for the problem with the short name \verb|test| must be in a class named \verb|test|, in a file named \verb|test.java|.
    %\textbf{Short names can be found on the grader as the problem title.}
    \item In an effort to give back feedback as soon as possible, automated responses are given for each submission. Feedback will consist of success or failure, along with reason for failure if applicable. We reserve the right to make final decisions on judging.
    \item If you have a question concerning a problem, you may submit a request for clarification through the grader interface.
    \item You are permitted to use any printed material that you have brought with you, including the official TJ IOI 2017 Study Guide.  You are also permitted to use the electronic documentation provided to you through the contest site. You many not collaborate with anyone outside of your team.
    \item Each team may use only one computer and all code must be written and submitted through this computer. If you are experiencing technical issues, alert a proctor and we will assist you.
    \item You are not permitted to access the Internet in any way other than accessing the contest site. You may not use any electronic or communications devices other than the computer. You may not intentionally exit the virtual machine for any reason. You may not attempt to attack or damage the grader. Breaking any of these rules may be grounds for disqualification.
    \item Good luck and have fun!
\end{enumerate}

\blank

\begin{center}
\textbf{\LARGE Do not turn the page until instructed to do so.}
\end{center}

%These are the official problems for the Thomas Jefferson Intermediate Olympiad in Informatics 2017.  This packet contains ten ($10$) problems, to be completed during the three ($3$) hour time period.  Once your time has expired, you will no longer be allowed to submit solutions.
%\blank
%Accepted languages include Java 8, Python 3, and C/C++.  Note that if you submit your code in Java, the name of the class in the file must match the name of the \texttt{.java} file.
%\blank
%Each team will be permitted to use one ($1$) computer, and all code must be written and submitted using the computer provided.  If you are experiencing technical issues during the contest, alert a proctor and we will assist you.
%\blank
%You are permitted to use any printed material that you have brought with you, including the official TJ IOI 2017 Study Guide.  You are also permitted to use the electronic documentation provided to you through the contest site.  As a team, you may collaborate among each other - however, you may not communicate with any other teams during the contest window for any reason.
%\blank
%You are not permitted to access the Internet in any way other than accessing the contest site.  No electronic devices other than the computer are permitted to be used, with the exception of a watch.  You may \textbf{not} intentionally exit the virtual machine for any reason.  Breaking any of these rules may be grounds for a disqualification.
%\blank
%Please do not submit any code that is not your own work.  We understand that many well-established algorithms do the job effectively, but if you are to use code that you did not write, please cite your sources with a comment.  Do \textbf{NOT} copy and paste large chunks of code.  Ultimately, the goal of TJ IOI is to help students foster a passion for computer science and to learn something new, and violations of personal or academic integrity defeat the purpose of the contest.
%\blank
%Do not turn this page and begin the contest until you are instructed to do so.  Good luck and have fun!